---
title: "Movie Data Manipulation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Setup

We are just going to first simply load in the various csv files(movies.csv, ratings.csv, tags.csv)

```{r cars}
library(tidyverse)

url_movies <- "C:/Users/Rahul/Documents/Summer 2020 Work/Movie Data/ml-latest/movies.csv"
movies_tab <- read_csv(url_movies)

url_ratings <- "C:/Users/Rahul/Documents/Summer 2020 Work/Movie Data/ml-latest/ratings.csv"
ratings_tab <- read_csv(url_ratings)

url_tags <- "C:/Users/Rahul/Documents/Summer 2020 Work/Movie Data/ml-latest/tags.csv"
tags_tab <- read_csv(url_tags)

url_links <- "C:/Users/Rahul/Documents/Summer 2020 Work/Movie Data/ml-latest/links.csv"
links_tab <- read_csv(url_links)

```

## Organize Data

Now that we have loaded in the datasets we can start to organize the data a little bit. First I will start out by averaging out the ratings for each movie and then sort them. I will also arrange the tags for each movie. After arranging the data properly I will combine all the necessary fields into 1 table. Then I will write the table into a csv file.

```{r tidy}
library(dplyr)
library(stats)

mean_ratings <- ratings_tab %>%
  select(movieId, rating) %>%
  group_by(movieId) %>%
  summarize(mean_rating = mean(rating)) %>%
  mutate_at(vars(starts_with("mean_rating")), funs(round(., 2))) %>%
  arrange(movieId)
mean_ratings

proper_tags <- tags_tab %>%
  select(movieId, tag) %>%
  group_by(movieId) %>%
  arrange(movieId)
proper_tags

one_link <- links_tab %>%
  select(movieId, imdbId, tmdbId)
one_link


adjusted <- merge(movies_tab, mean_ratings, by = "movieId")
adjusted <- merge(adjusted, one_link, by = "movieId")
head(adjusted, 10)

write.csv(adjusted,"C:/Users/Rahul/Documents/Summer 2020 Work/Movie Data/ml-latest/final.csv", row.names = FALSE)

```

Now that I have the data in a new csv file I can start to implement the movie recommendation system through Java.
